Creation of a DRN shapefile with associated capacities

### 2022-03-22 R/Core_code/DRN_operations/2_New_hdrn.Rmd
DRN processing uèdate

```{r}
path <- "C:/Thesis_fortran/WASA/shapefile/Banabuiu"
main_resI <- st_read(paste0(path, "/mainreservoirsI_cut_ref.shp"))
main_resII <- st_read(paste0(path, "/mainreservoirsII_cut_ref.shp"))

threshold <- min(main_resI$AREA)
glob_wat_cut <- global_water[which(global_water$area_geom < threshold),]

@@

DN = 1 means that in that element water is present. Removing the shapes which present DN = 0 is then useful for the next step in QGIS (the NNJoin), so that the HDRN points will not be matched with the areas which don't present water in them.

```{r}
glob_wat_cut<-glob_wat_cut[which(glob_wat_cut$DN == 1),]
```

@@

```{r}
writeOGR(glob_wat_cut,dsn = "./Global_surface_water/shape", layer = "global_wat_cut",
         driver = "ESRI Shapefile" )
```

# HDRN update

@@

```{r load HDRN to update}
HDRN_update<-readOGR(dsn = "./HDRN/HDRN_update_area_ID.shp")
```

@@

k <- damk_Molle <- 1500
a <- alpha_Molle <- 2.7

HDRN_update$capacity<-k*(HDRN_update$join_area_/(a*k))^(a/(a-1)) #m3

#Area = a*k*(100000/k)^((a-1)/a)

#Reservoirs classes definition
# res_class<-c(
#               102179,
#               151360,
#               265735,
#               758010,
#               875797530
#             )
#this classification doesn't make any sense with the values we have
#quantile(HDRN_update$capacity, probs = seq(0, 1, 0.2))

#cap_glob<-k*(glob_wat_cut$area_geom/(a*k))^(a/(a-1))
#quantile(cap_glob, probs = seq(0, 1, 0.2))

#Reservoirs classes definition
#From Mamede et al. 2018
res_class<-c(
              5000, #m3
              25000,
              50000,
              100000,
              max(HDRN_update$capacity)+1
            )

@@

Find the HDRN's reservoirs (id) that present the same Global Water reservoir (join_fid). To the one with the highest distance, associate the capacity of the smallest reservoir class

@@

tic("Lowest reservoir class to points with no associate global water")
subset<-HDRN_update[duplicated(HDRN_update$join_fid),]
for(i in 1:length(subset$join_fid)){
  #Take the first duplicate ID
  check1<-subset$join_fid[i] 
  #Take the minimum distance from the points with the same associated ID
  check2<-min(HDRN_update$distance[HDRN_update$join_fid %in% check1])
  #Take the point associated to the minimum distance
  check3<-HDRN_update$id[which(HDRN_update$join_fid %in% check1 & HDRN_update$distance == check2)]

  #Associate the lowest reservoir class to the points with distance higher
  #than check2
  HDRN_update$capacity[which(HDRN_update$join_fid %in% check1
                             & HDRN_update$distance > check2
                             & HDRN_update$id != check3)]<-res_class[1]-0.1
}
remove(subset, check1, check2, check3)
toc()

summary(HDRN_update@data)

#Export the updated HDRN
# writeOGR(HDRN_update,dsn = "./HDRN", layer = "HDRN_afterR_v1",
#          driver = "ESRI Shapefile")
```

@@

tic("Removal of points with no associated global water")
subset<-HDRN_update[duplicated(HDRN_update$join_fid),] #Finds the duplicates
for(i in 1:length(subset$join_fid)){
  #Take the first duplicate ID
  check1<-subset$join_fid[i] 
  #Take the minimum distance from the points with the same associated ID
  check2<-min(HDRN_update$distance[HDRN_update$join_fid %in% check1])
  #Take the point associated to the minimum distance
  check3<-HDRN_update$id[which(HDRN_update$join_fid %in% check1 & HDRN_update$distance == check2)]

  #Remove the duplicate points with a distance higher than check2
  HDRN_update<-HDRN_update[which(!(HDRN_update$join_fid %in% check1
                                      & HDRN_update$distance > check2
                                      & HDRN_update$id != check3)),]
}
remove(subset, check1, check2, check3)
toc()

summary(HDRN_update@data)

#Export the updated HDRN
# writeOGR(HDRN_update,dsn = "./HDRN", layer = "HDRN_afterR_v2",
#          driver = "ESRI Shapefile" )
```

@@

#Load the updated HDRN
#Method 1 (Unidentified reservoirs associated to the lowest class)
# path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/HDRN/HDRN_afterR_v1.shp"
#Method 2 (Unidentified reservoirs removed)
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/HDRN/HDRN_afterR_v2.shp"

HDRN_update<-readOGR(path)

@@

for(i in 1:5){
  if(i != 1){
    c <- HDRN_update@data %>%
          filter(!is.na(SubbasinID)) %>%
          group_by(SubbasinID) %>%
      #   filter(capacity <= res_class[i+1] & capacity > res_class[i]) %>%
      #for Mamede classification: below
          filter(capacity < res_class[i] & capacity >= res_class[i-1]) %>%
          summarize(count=n())
  }else{
    c <- HDRN_update@data %>%
          filter(!is.na(SubbasinID)) %>%
          group_by(SubbasinID) %>%
          #filter(capacity <= res_class[i+1]) %>%
      #for Mamede classification: below
          filter(capacity < res_class[i]) %>%
          summarize(count=n())
  }
  for(a in 1:length(c$SubbasinID)){
    for(b in 1:length(count_class$SubbasinID)){
        if(c$SubbasinID[a]==count_class$SubbasinID[b]) count_class[b,i+1]<-c$count[a]
    }
  }
}
names(count_class)<-c("SubbasinID","class1","class2","class3","class4","class5")
count_class[is.na(count_class)]<-0

#Class ripartition
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
count_class<-read.table(paste0(path, "/lake_number_newHDRN_met2.dat"), skip = 2)

@@

```{r lake_number}
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
my.write(count_class,file=paste0(path,"/lake_number_newHDRN_met2.dat"),
         header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",f = write.table)
```

@@

for(i in 1:5){
  if(i != 1){
    c <- HDRN_update@data %>%
          filter(!is.na(SubbasinID)) %>%
          group_by(SubbasinID) %>%
      #   filter(capacity <= res_class[i+1] & capacity > res_class[i]) %>%
      #for Mamede classification: below
          filter(capacity < res_class[i] & capacity >= res_class[i-1]) %>%
          summarize(median(capacity))
  }else{
    c <- HDRN_update@data %>%
          filter(!is.na(SubbasinID)) %>%
          group_by(SubbasinID) %>%
          #filter(capacity <= res_class[i+1]) %>%
      #for Mamede classification: below
          filter(capacity < res_class[i]) %>%
          summarize(median(capacity))
  }
  for(a in 1:length(c$SubbasinID)){
    for(b in 1:length(median_class$SubbasinID)){
        if(c$SubbasinID[a]==median_class$SubbasinID[b]) median_class[b,i+1]<-c$`median(capacity)`[a]
    }
  }
}
names(median_class)<-c("SubbasinID","class1","class2","class3","class4","class5")
median_class[is.na(median_class)]<-0
```

```{r export lake_maxvol}
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
my.write(round(median_class,2),file=paste0(path,"/lake_maxvol_newHDRN_m2_median.dat"),
         header = "Specification of water storage capacity for the reservoir size classes\nSub-basin-ID, maxlake[m**3] (five reservoir size classes)",f = write.table)
```

# Scenario without the HDRN

@@

```{r no HDRN lake}
#Dataframe construction
par_class<-data.frame(seq(1,5,1),     #Reservoir_class-ID
                      round(res_class,2),      #maxlake0
                      rep(1,5),       #lake_vol0_factor
                      rep(0,5),       #lake_change: leave it to 0, so the number of reservoirs doesn't increase
                      rep(alpha_Molle,5),   
                      rep(damk_Molle,5),
                      c(12.5,18.75,25,37.5,50),       #damc_hrr
                      rep(1.5,5)      #damd_hrr
                      )
names(par_class)<-c("Reservoir_class-ID", "maxlake0_m3", "lake_vol0_factor", "lake_change", "alpha_Molle", "damk_Molle", "damc_hrr", "damd_hrr")

#Save it
options(scipen = 999)
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
my.write(par_class,file=paste0(path,"/lake_noHDRN.dat"),
         header = "Specification of parameters for the reservoir size classes\nReservoir_class-ID, maxlake0[m**3], lake_vol0_factor[-], lake_change[-], alpha_Molle[-], damk_Molle[-], damc_hrr[-], damd_hrr[-]",f = write.table)
options(scipen = 0)
```

```{r no HDRN lake_number}
#Sub-basins without networks of small reservoirs must not be entered in the file.
#Create a blank file and try if it works
#Otherwise, create a file with only 1 reservoir for each subbasin, in the lowest class

#No reservoirs
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
write.table("Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",paste0(path,"/lake_number_noHDRN_v1.dat"), row.names = FALSE, quote = FALSE, col.names = FALSE)

#Only one resevoir in the smallest reservoir class
count_class[,2]<-1
count_class[,3:6]<-0
my.write(count_class,file=paste0(path,"/lake_number_noHDRN_v2.dat"),
         header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",f = write.table)

#Only zeros
#it works!!!!
count_class[,2]<-0
count_class[,3:6]<-0
my.write(count_class,file=paste0(path,"/lake_number_noHDRN_v3.dat"),
         header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",f = write.table)

>>>>

```{r}
main_resI <- st_read("./Data/Shapefile/Reservoirs/mainreservoirsI_cut_ref.shp")
main_resII <- st_read("./Data/Shapefile/Reservoirs/mainreservoirsII_cut_ref.shp")

threshold <- min(main_resI$AREA)
glob_wat_cut <- global_water[which(global_water$area_geom < threshold),]
```

@@

DN = 1 means that in that element water is present. Removing the shapes which present DN = 0 is then useful for the next step in QGIS (the NNJoin), so that the DRN points will not be matched with the areas which don't present water in them.

```{r}
glob_wat_cut <- glob_wat_cut[which(glob_wat_cut$DN == 1),]
```

@@

```{r}
writeOGR(glob_wat_cut, dsn = "./Global_surface_water", layer = "global_wat_cut",
         driver = "ESRI Shapefile" )
```

# DRN update

@@

```{r load DRN to update}
DRN_update <- readOGR(dsn = "./DRN/DRN_update_area_ID.shp")
```

@@

k <- damk_Molle <- 1500
a <- alpha_Molle <- 2.7
DRN_update$capacity <- k*(DRN_update$join_area_/(a*k))^(a/(a-1)) #m3

#Reservoirs classes definition
#From Mamede et al. 2018
res_class<-c(
              5000, #m3
              25000,
              50000,
              100000,
              max(DRN_update$capacity)+1
            )
```

@@

Find the DRN's reservoirs (id) that present the same Global Water reservoir (join_fid). To the one with the highest distance, associate the capacity of the smallest reservoir class

@@

tic("Lowest reservoir class to points with no associate global water")
subset <- DRN_update[duplicated(DRN_update$join_fid),]
for(i in seq_len(length(subset$join_fid))){
  #Take the first duplicate ID
  check1 <- subset$join_fid[i] 
  #Take the minimum distance from the points with the same associated ID
  check2 <- min(DRN_update$distance[DRN_update$join_fid %in% check1])
  #Take the point associated to the minimum distance
  check3 <- DRN_update$id[which(DRN_update$join_fid %in% check1 & DRN_update$distance == check2)]

  #Associate the lowest reservoir class to the points with distance higher
  #than check2
  DRN_update$capacity[which(DRN_update$join_fid %in% check1
                             & DRN_update$distance > check2
                             & DRN_update$id != check3)] <- res_class[1] - 0.1
}
remove(subset, check1, check2, check3)
toc()

summary(DRN_update@data)

#Export the updated DRN
# writeOGR(DRN_update,dsn = "./DRN", layer = "DRN_afterR_v1",
#          driver = "ESRI Shapefile")
```

@@

tic("Removal of points with no associated global water")
subset <- DRN_update[duplicated(DRN_update$join_fid),] #Finds the duplicates
for(i in seq_len(length(subset$join_fid))){
  #Take the first duplicate ID
  check1 <- subset$join_fid[i] 
  #Take the minimum distance from the points with the same associated ID
  check2 <- min(DRN_update$distance[DRN_update$join_fid %in% check1])
  #Take the point associated to the minimum distance
  check3 <- DRN_update$id[which(DRN_update$join_fid %in% check1 & DRN_update$distance == check2)]

  #Remove the duplicate points with a distance higher than check2
  DRN_update <- DRN_update[which(!(DRN_update$join_fid %in% check1
                                      & DRN_update$distance > check2
                                      & DRN_update$id != check3)),]
}
remove(subset, check1, check2, check3)
toc()

summary(DRN_update@data)

#Export the updated DRN
# writeOGR(DRN_update,dsn = "./DRN", layer = "DRN_afterR_v2",
#          driver = "ESRI Shapefile" )
```

@@

#Load the updated DRN
#Method 1 (Unidentified reservoirs associated to the lowest class)
# path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/DRN/DRN_afterR_v1.shp"
#Method 2 (Unidentified reservoirs removed)
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Data/DRN/DRN_afterR_v2.shp"

DRN_update<-readOGR(path)

@@

for(i in 1:5){
  if(i != 1){
    c <- DRN_update@data %>%
          filter(!is.na(SubbasinID)) %>%
          group_by(SubbasinID) %>%
      #   filter(capacity <= res_class[i+1] & capacity > res_class[i]) %>%
      #for Mamede classification: below
          filter(capacity < res_class[i] & capacity >= res_class[i-1]) %>%
          summarize(count=n())
  }else{
    c <- DRN_update@data %>%
          filter(!is.na(SubbasinID)) %>%
          group_by(SubbasinID) %>%
          #filter(capacity <= res_class[i+1]) %>%
      #for Mamede classification: below
          filter(capacity < res_class[i]) %>%
          summarize(count=n())
  }
  for(a in seq_len(length(c$SubbasinID))){
    for(b in seq_len(length(count_class$SubbasinID))){
        if(c$SubbasinID[a] == count_class$SubbasinID[b]) count_class[b,i+1] <- c$count[a]
    }
  }
}
names(count_class) <- c("SubbasinID","class1","class2","class3","class4","class5")
count_class[is.na(count_class)] <- 0

#Class ripartition
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
count_class<-read.table(paste0(path, "/lake_number_newDRN_met2.dat"), skip = 2)

@@

```{r lake_number}
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
my.write(count_class,file=paste0(path,"/lake_number_newDRN_met2.dat"),
         header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",f = write.table)
```

@@

for(i in 1:5){
  if(i != 1){
    c <- DRN_update@data %>%
          filter(!is.na(SubbasinID)) %>%
          group_by(SubbasinID) %>%
      #   filter(capacity <= res_class[i+1] & capacity > res_class[i]) %>%
      #for Mamede classification: below
          filter(capacity < res_class[i] & capacity >= res_class[i-1]) %>%
          summarize(median(capacity))
  }else{
    c <- DRN_update@data %>%
          filter(!is.na(SubbasinID)) %>%
          group_by(SubbasinID) %>%
          #filter(capacity <= res_class[i+1]) %>%
      #for Mamede classification: below
          filter(capacity < res_class[i]) %>%
          summarize(median(capacity))
  }
  for(a in 1:length(c$SubbasinID)){
    for(b in 1:length(median_class$SubbasinID)){
        if(c$SubbasinID[a]==median_class$SubbasinID[b]) median_class[b,i+1]<-c$`median(capacity)`[a]
    }
  }
}
names(median_class)<-c("SubbasinID","class1","class2","class3","class4","class5")
median_class[is.na(median_class)]<-0
```

```{r export lake_maxvol}
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
my.write(round(median_class,2),file=paste0(path,"/lake_maxvol_newDRN_m2_median.dat"),
         header = "Specification of water storage capacity for the reservoir size classes\nSub-basin-ID, maxlake[m**3] (five reservoir size classes)",f = write.table)
```

# Scenario without the DRN

@@

```{r no DRN lake}
#Dataframe construction
par_class<-data.frame(seq(1,5,1),     #Reservoir_class-ID
                      round(res_class,2),      #maxlake0
                      rep(1,5),       #lake_vol0_factor
                      rep(0,5),       #lake_change: leave it to 0, so the number of reservoirs doesn't increase
                      rep(alpha_Molle,5),   
                      rep(damk_Molle,5),
                      c(12.5,18.75,25,37.5,50),       #damc_hrr
                      rep(1.5,5)      #damd_hrr
                      )
names(par_class)<-c("Reservoir_class-ID", "maxlake0_m3", "lake_vol0_factor", "lake_change", "alpha_Molle", "damk_Molle", "damc_hrr", "damd_hrr")

#Save it
options(scipen = 999)
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
my.write(par_class,file=paste0(path,"/lake_noDRN.dat"),
         header = "Specification of parameters for the reservoir size classes\nReservoir_class-ID, maxlake0[m**3], lake_vol0_factor[-], lake_change[-], alpha_Molle[-], damk_Molle[-], damc_hrr[-], damd_hrr[-]",f = write.table)
options(scipen = 0)
```

```{r no DRN lake_number}
#Sub-basins without networks of small reservoirs must not be entered in the file.
#Create a blank file and try if it works
#Otherwise, create a file with only 1 reservoir for each subbasin, in the lowest class

#No reservoirs
path<-"C:/Users/Utente/OneDrive - Politecnico di Milano/Backup PC/Uni/Thesis/Analysis/gen_files"
write.table("Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",paste0(path,"/lake_number_noDRN_v1.dat"), row.names = FALSE, quote = FALSE, col.names = FALSE)

#Only one resevoir in the smallest reservoir class
count_class[,2]<-1
count_class[,3:6]<-0
my.write(count_class,file=paste0(path,"/lake_number_noDRN_v2.dat"),
         header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",f = write.table)

#Only zeros
#it works!!!!
count_class[,2]<-0
count_class[,3:6]<-0
my.write(count_class,file=paste0(path,"/lake_number_noDRN_v3.dat"),
         header = "Specification of total number of reservoirs in the size classes\nSub-basin-ID, acud[-] (five reservoir size classes)",f = write.table)
